Spin canonical rings of log stacky curves

### 2015-07-02 stacky_write_up/spin_cring.tex

We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions \ref{custom:sat-1-*}, \ref{custom:sat-1-**}, and \ref{custom:sat-1-***}.  Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among pole orders of the $y_i$'s) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition \ref{custom:sat-1-*}.  Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above implies \ref{custom:sat-1-**}.  Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{a_j}\in S$, condition \ref{custom:sat-1-***} holds.  Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$.

>>>>

\todo{Say something like a monomial is in $S$ if and only if it satisfies some condition with $c_h,$ and that we use this to check the three (*) conditions.}
We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions \ref{custom:sat-1-*}, \ref{custom:sat-1-**}, and \ref{custom:sat-1-***}.  Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among $c_1, \ldots, c_n$) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition \ref{custom:sat-1-*}.  Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above implies \ref{custom:sat-1-**}.  Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{a_j}\in S$, condition \ref{custom:sat-1-***} holds.  Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$.
